---
title: "Neurocognitive mechanisms of population-level virality" 
author: "Scholz, C., Baek, E.C., O'Donnell M.B., Kim, H.S., Cappella, J.N., Falk, E.B."
date: "January 9, 2017"
output: 
  html_document:
    toc: true
    theme: paper
    highlight: textmate
---

#Citation

Scholz, C., Baek, E.C., O'Donnell M.B., Kim, H.S., Cappella, J.N., Falk, E.B. (in press). Neurocognitive mechanisms of population-level virality. PNAS

Keywords: Information sharing, virality, fMRI, population-level behavior, psychological mechanisms

# Load R packages
```{r,echo=FALSE}
library('lavaan')
library('mediation')
library('lmerTest')
library('pbkrtest')
library('car')
```

# Data

Dataframes necessary to produce the results reported in the paper are read in below

```{r,echo=FALSE}
# Article data
articles<-read.csv('data/articles.csv',stringsAsFactors = F)

# Create ranked population-level retransmission variable
articles$rank_ret=rank(articles$retransmit_total)

# Study 1 data
## Demographics
demo_study1<-read.csv('data/demographics_study1.csv',stringsAsFactors = F)

## Neural Data

### Ranked data
s1_read<-read.csv('data/study1_red_to_read.csv')

### Unranked data
s1_read_raw<-read.csv('data/study1_red_to_read_raw.csv')

### Merge Study 1 neural data with article data
s1_read<-merge(s1_read,articles)
s1_read_raw<-merge(s1_read_raw,articles)

# Study 2 data

## Demographics
demo_study2<-read.csv('data/demographics_study2.csv',stringsAsFactors = F)

## Neural Data
### Ranked
s2_abstract<-read.csv('data/study2_red_to_abstract.csv',stringsAsFactors = F)

### Unranked
s2_abstract_raw<-read.csv('data/study2_red_to_abstract_raw.csv',stringsAsFactors = F)

### Combine neural and article data
s2_abstract<-merge(s2_abstract,articles)
s2_abstract_raw<-merge(s2_abstract_raw,articles)

### Dataset for analysis of other task conditions
# study 1 data
s1_broad<-read.csv('data/study1_red_to_broad.csv',stringsAsFactors = F)
s1_narrow<-read.csv('data/study1_red_to_narrow.csv',stringsAsFactors = F)

s1_narrow<-merge(s1_narrow,articles)
s1_broad<-merge(s1_broad,articles)
```

# Descriptives

* Study 1 participants: 
  + N =`r length(unique(demo_study1$pID))`
  + `r sum(demo_study1$gender==2)` females
  + Age: M = `r mean(demo_study1$age)`, SD = `r sd(demo_study1$age)`, Range = `r min(demo_study1$age)` to `r max(demo_study1$age)`
* Study 2 participants: 
  + N =`r length(unique(demo_study2$pID))`
  + `r sum(demo_study2$gender==2)` females
  + Age: M = `r mean(demo_study2$age)`, SD = `r sd(demo_study2$age)`, Range = `r min(demo_study2$age)` to `r max(demo_study2$age)` 
* Number of articles Study 1: `r length(unique(articles$art_id))`
* Number of articles Study 2: `r sum(!is.na(s2_abstract$self))`
* Retransmission counts: 
  + Total number: `r sum(articles$retransmit_total)`
  + Mean: `r mean(articles$retransmit_total)`
  + SD: `r sd(articles$retransmit_total)`
  + Range: `r min(articles$retransmit_total)` to `r max(articles$retransmit_total)`
- Article word count (headlines and abstracts): 
  + Mean: `r mean(articles$total_wc)`
  + SD: `r sd(articles$total_wc)`
  + Range: `r min(articles$total_wc)` to `r max(articles$total_wc)`
- Study 1 Article Task article presentation times:
  + `r min(articles$pres_time)` sec: N = `r sum(articles$pres_time==8)`
  + `r unique(articles$pres_time)[1]` sec: N = `r sum(articles$pres_time==10)`
  + `r max(articles$pres_time)` sec: N = `r sum(articles$pres_time==12)`

# Results

## Figure 1
```{r}
# Path model
mod<-'rank_ret~c*value+mentalizing_reduced+self
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
```

Study 1 Path model 
```{r}
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)
```

Study 2 Path model
```{r}
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T, standardized=T)
```

Indirect effects (with bias-corrected confidence intervals)

Study 1 - Social cognition
```{r}
out.fit<-lm(rank_ret~value+mentalizing_reduced+self, data=s1_read)
med.fit<-lm(value~mentalizing_reduced+self, data=s1_read)

med.out <- mediate(med.fit, out.fit, treat = "mentalizing_reduced", covariate="self", mediator = "value", sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med.out)
```

Study 1 Self-related processing
```{r}
med2.out <- mediate(med.fit, out.fit, treat = "self", mediator = "value", covariate='mentalizing_reduced', sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med2.out)
```

Study 2 - Social Cognition
````{r}
out.fit<-lm(rank_ret~value+mentalizing_reduced+self, data=s2_abstract)
med.fit<-lm(value~mentalizing_reduced+self, data=s2_abstract)

# Estimate the indirect effect, specifying mentalizing as the independent variable and self as a covariate
med.out <- mediate(med.fit, out.fit, treat = "mentalizing_reduced", covariate="self", mediator = "value", sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med.out)
```

Study 2 - Self-related processing
```{r}
med2.out <- mediate(med.fit, out.fit, treat = "self", mediator = "value", covariate='mentalizing_reduced', sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med2.out)
```

# Supporting Information

## Figures and Tables

### Figure S2 (unranked variables)

Log-transform retransmission variable to normality

```{r}
s1_read_raw$retransmit_log<-log(s1_read_raw$retransmit_total)
s2_abstract_raw$retransmit_log<-log(s2_abstract_raw$retransmit_total)
```

Path Model
```{r}
mod<-'retransmit_log~c*value+mentalizing_reduced+self
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
```

Study 1
```{r}
mod.fit<-sem(mod,data=s1_read_raw)
summary(mod.fit,rsquare=T, standardized=T)
```

Study 2
```{r}
mod.fit<-sem(mod,data=s2_abstract_raw)
summary(mod.fit,rsquare=T, standardized=T)
```

Indirect Effects - Bias corrected confidence intervals

Study 1 - Social cognition
```{r}
out.fit<-lm(retransmit_log~value+mentalizing_reduced+self, data=s1_read_raw)
med.fit<-lm(value~mentalizing_reduced+self, data=s1_read_raw)

med.out <- mediate(med.fit, out.fit, treat = "mentalizing_reduced", covariate="self", mediator = "value", sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med.out)
```

Study 1 - Self-Related Processing
```{r}
med2.out <- mediate(med.fit, out.fit, treat = "self", mediator = "value", covariate='mentalizing_reduced', sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med2.out)
```

Study 2 - Social cognition
```{r}
out.fit<-lm(retransmit_log~value+mentalizing_reduced+self, data=s2_abstract_raw)
med.fit<-lm(value~mentalizing_reduced+self, data=s2_abstract_raw)

med.out <- mediate(med.fit, out.fit, treat = "mentalizing_reduced", covariate="self", mediator = "value", sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med.out)
```

Study 2 - Self-related processing
```{r}
med2.out <- mediate(med.fit, out.fit, treat = "self", mediator = "value", covariate='mentalizing_reduced', sims = 1000, boot=T, boot.ci.type= 'bca')
summary(med2.out)
```

# Figure S4

Effect of intention on retransmission

```{r}
mod<-'rank_ret~mean_share_rating_rank'
```

Study 1
```{r}
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, standardized=T)
```

Study 2
```{r}
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, standardized=T)
```

Value-based virality controlling for intention

```{r}
mod<-'rank_ret~c*value+mentalizing_reduced+self+mean_share_rating_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
```

Study 1
```{r}
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, standardized=T)
```

Study 2
```{r}
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, standardized=T)
```

## Table S2

Study 1
```{r}
cor.test(s1_read$self,s1_read$mentalizing_reduced)
cor.test(s1_read$self,s1_read$value)
cor.test(s1_read$self,s1_read$rank_ret)
cor.test(s1_read$self,s1_read$mean_share_rating_rank)

cor.test(s1_read$mentalizing_reduced,s1_read$value)
cor.test(s1_read$mentalizing_reduced,s1_read$rank_ret)
cor.test(s1_read$mentalizing_reduced,s1_read$mean_share_rating_rank)

cor.test(s1_read$value,s1_read$rank_ret)
cor.test(s1_read$value,s1_read$mean_share_rating_rank)

cor.test(s1_read$rank_ret,s1_read$mean_share_rating_rank)
```

Study 2
```{r}
cor.test(s2_abstract$self,s2_abstract$mentalizing_reduced)
cor.test(s2_abstract$self,s2_abstract$value)
cor.test(s2_abstract$self,s2_abstract$rank_ret)
cor.test(s2_abstract$self,s2_abstract$mean_share_rating_rank)

cor.test(s2_abstract$mentalizing_reduced,s2_abstract$value)
cor.test(s2_abstract$mentalizing_reduced,s2_abstract$rank_ret)
cor.test(s2_abstract$mentalizing_reduced,s2_abstract$mean_share_rating_rank)

cor.test(s2_abstract$value,s2_abstract$rank_ret)
cor.test(s2_abstract$value,s2_abstract$mean_share_rating_rank)

cor.test(s2_abstract$rank_ret,s2_abstract$mean_share_rating_rank)
```

## Table S3

Study 1
```{r}
cor.test(s1_read_raw$self,s1_read_raw$mentalizing_reduced)
cor.test(s1_read_raw$self,s1_read_raw$value)
cor.test(s1_read_raw$self,s1_read_raw$retransmit_log)

cor.test(s1_read_raw$mentalizing_reduced,s1_read_raw$value)
cor.test(s1_read_raw$mentalizing_reduced,s1_read_raw$retransmit_log)

cor.test(s1_read_raw$value,s1_read_raw$retransmit_log)
```

Study 2
```{r}
cor.test(s2_abstract_raw$self,s2_abstract_raw$mentalizing_reduced)
cor.test(s2_abstract_raw$self,s2_abstract_raw$value)
cor.test(s2_abstract_raw$self,s2_abstract_raw$retransmit_log)

cor.test(s2_abstract_raw$mentalizing_reduced,s2_abstract_raw$value)
cor.test(s2_abstract_raw$mentalizing_reduced,s2_abstract_raw$retransmit_log)

cor.test(s2_abstract_raw$value,s2_abstract_raw$retransmit_log)
```

## Table S4

(A) Valuation mediates

```{r}
value_med<-'rank_ret~c*value
value~a*self+b*mentalizing_reduced
indirect_mentalizing := b*c
indirect_self := a*c'
```

Study 1
```{r}
value_med.fit<-sem(value_med,data=s1_read)
summary(value_med.fit,rsquare=T, standardized=T,fit.measures=T)
```

Study 2
```{r}
value_med.fit<-sem(value_med,data=s2_abstract)
summary(value_med.fit,rsquare=T, standardized=T,fit.measures=T)
```

(B) Self-related processing mediates

```{r}
self_med<-'rank_ret~c*self
self~a*value+b*mentalizing_reduced
indirect_mentalizing := b*c
indirect_value := a*c'
```

Study 1
```{r}
self_med.fit<-sem(self_med,data=s1_read)
summary(self_med.fit,rsquare=T, standardized=T,fit.measures=T)
```

Study 2
```{r}
self_med.fit<-sem(self_med,data=s2_abstract)
summary(self_med.fit,rsquare=T, standardized=T,fit.measures=T)
```

(C) Social cognition mediates
```{r}
social_med<-'rank_ret~c*mentalizing_reduced
mentalizing_reduced~a*self+b*value
indirect_value := b*c
indirect_self := a*c'
```

Study 1
```{r}
social_med.fit<-sem(social_med,data=s1_read)
summary(social_med.fit,rsquare=T, standardized=T,fit.measures=T)
```

Study 2
```{r}
social_med.fit<-sem(social_med,data=s2_abstract)
summary(social_med.fit,rsquare=T, standardized=T,fit.measures=T)
```

# Analysis of other article task conditions

Narrowcasting

```{r}
cor.test(s1_narrow$value,s1_narrow$rank_ret)
```

Broadcasting

```{r}
cor.test(s1_broad$value,s1_broad$rank_ret)
```

Variances of value-related processing in read, narrow-, and broadcasting conditions

* Reading condition: s2 = `r var(s1_read$value)`
* Narrocasting condition: s2 = `r var(s1_narrow$value)` 
* Broadcasting condition: s2 = `r var(s1_broad$value)`

## Analysis of Article Characteristics

Rank article characteristics variables (except dichotomous variables)

```{r}
# Study 1
s1_read$useful_rank<-rank(s1_read$useful)
s1_read$positivity_word_rank<-rank(s1_read$positivity_word)
s1_read$positivity_sv_rank<-rank(s1_read$positivity_sv)
s1_read$controversial_rank<-rank(s1_read$controversial)
s1_read$novelty_rank<-rank(s1_read$novelty)
s1_read$aroused_rank<-rank(s1_read$aroused)
s1_read$ln_emotionality_word_rank<-rank(s1_read$ln_emotionality_word)

# Study 2
s2_abstract$useful_rank<-rank(s2_abstract$useful)
s2_abstract$positivity_word_rank<-rank(s2_abstract$positivity_word)
s2_abstract$positivity_sv_rank<-rank(s2_abstract$positivity_sv)
s2_abstract$controversial_rank<-rank(s2_abstract$controversial)
s2_abstract$novelty_rank<-rank(s2_abstract$novelty)
s2_abstract$aroused_rank<-rank(s2_abstract$aroused)
s2_abstract$ln_emotionality_word_rank<-rank(s2_abstract$ln_emotionality_word)
```

Value-based virality controlling for individual article characteristics

```{r}
# Useful
mod<-'rank_ret~c*value+useful_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# efficacy
mod<-'rank_ret~c*value+efficacy
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# Disease
mod<-'rank_ret~c*value+disease
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# positivity_sv
mod<-'rank_ret~c*value+positivity_sv_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# Positivity_word
mod<-'rank_ret~c*value+positivity_word_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# aroused
mod<-'rank_ret~c*value+aroused_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# novelty
mod<-'rank_ret~c*value+novelty_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# ln_emotionality_word
mod<-'rank_ret~c*value+ln_emotionality_word_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

# controversial
mod<-'rank_ret~c*value+controversial_rank
value~a*mentalizing_reduced+b*self
indirect_mentalizing_reduced := a*c
indirect_self := b*c
'
## Study 1
mod.fit<-sem(mod,data=s1_read)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)

## Study 2
mod.fit<-sem(mod,data=s2_abstract)
summary(mod.fit,rsquare=T, fit.measures=T,standardized=T)
```

Relationships between individual article characteristics, self-related and social-cognition

Self-related processing - Study 1
```{r}
cor.test(s1_read$positivity_sv_rank,s1_read$self)

leveneTest(s1_read$self,s1_read$disease)
t.test(s1_read$self[s1_read$disease==0],s1_read$self[s1_read$disease==1],var.equal = T)

cor.test(s1_read$useful_rank,s1_read$self)
cor.test(s1_read$positivity_word_rank,s1_read$self)
cor.test(s1_read$aroused_rank,s1_read$self)
cor.test(s1_read$novelty_rank,s1_read$self)
cor.test(s1_read$controversial_rank,s1_read$self)
cor.test(s1_read$ln_emotionality_word_rank,s1_read$self)

leveneTest(s1_read$efficacy,s1_read$self)
t.test(s1_read$self[s1_read$efficacy==0],s1_read$self[s1_read$efficacy==1],var.equal = T)
```

Self-related processing - Study 2
```{r}
cor.test(s2_abstract$positivity_sv_rank,s2_abstract$self)

leveneTest(s2_abstract$self,s2_abstract$disease)
t.test(s2_abstract$self[s2_abstract$disease==0],s2_abstract$self[s2_abstract$disease==1],var.equal = T)

cor.test(s2_abstract$useful_rank,s2_abstract$self)
cor.test(s2_abstract$positivity_word_rank,s2_abstract$self)
cor.test(s2_abstract$aroused_rank,s2_abstract$self)
cor.test(s2_abstract$novelty_rank,s2_abstract$self)
cor.test(s2_abstract$controversial_rank,s2_abstract$self)
cor.test(s2_abstract$ln_emotionality_word_rank,s2_abstract$self)

leveneTest(s2_abstract$efficacy,s2_abstract$self)
t.test(s2_abstract$self[s2_abstract$efficacy==0],s2_abstract$self[s2_abstract$efficacy==1],var.equal = T)
```

Social Processing - Study 1

```{r}
cor.test(s1_read$positivity_sv_rank,s1_read$mentalizing_reduced)

leveneTest(s1_read$mentalizing_reduced,s1_read$disease)
t.test(s1_read$mentalizing_reduced[s1_read$disease==0],s1_read$mentalizing_reduced[s1_read$disease==1],var.equal = T)

cor.test(s1_read$useful_rank,s1_read$mentalizing_reduced)
cor.test(s1_read$positivity_word_rank,s1_read$mentalizing_reduced)
cor.test(s1_read$aroused_rank,s1_read$mentalizing_reduced)
cor.test(s1_read$novelty_rank,s1_read$mentalizing_reduced)
cor.test(s1_read$controversial_rank,s1_read$mentalizing_reduced)
cor.test(s1_read$ln_emotionality_word_rank,s1_read$mentalizing_reduced)

leveneTest(s1_read$efficacy,s1_read$mentalizing_reduced)
t.test(s1_read$mentalizing_reduced[s1_read$efficacy==0],s1_read$mentalizing_reduced[s1_read$efficacy==1],var.equal = F)
```
Social Processing - Study 2

```{r}
cor.test(s2_abstract$positivity_sv_rank,s2_abstract$mentalizing_reduced)

leveneTest(s2_abstract$mentalizing_reduced,s2_abstract$disease)
t.test(s2_abstract$mentalizing_reduced[s2_abstract$disease==0],s2_abstract$mentalizing_reduced[s2_abstract$disease==1],var.equal = F)

cor.test(s2_abstract$useful_rank,s2_abstract$mentalizing_reduced)
cor.test(s2_abstract$positivity_word_rank,s2_abstract$mentalizing_reduced)
cor.test(s2_abstract$aroused_rank,s2_abstract$mentalizing_reduced)
cor.test(s2_abstract$novelty_rank,s2_abstract$mentalizing_reduced)
cor.test(s2_abstract$controversial_rank,s2_abstract$mentalizing_reduced)
cor.test(s2_abstract$ln_emotionality_word_rank,s2_abstract$mentalizing_reduced)

leveneTest(s2_abstract$efficacy,s2_abstract$mentalizing_reduced)
t.test(s2_abstract$mentalizing_reduced[s2_abstract$efficacy==0],s2_abstract$mentalizing_reduced[s2_abstract$efficacy==1],var.equal = T)
```

## Relationship between value-related activity and article characteristics 


Study 21
```{r}
cor.test(s1_read$positivity_sv_rank,s1_read$value)

leveneTest(s1_read$value,s1_read$disease)
t.test(s1_read$value[s1_read$disease==0],s1_read$value[s1_read$disease==1],var.equal = T)

cor.test(s1_read$useful_rank,s1_read$value)
cor.test(s1_read$positivity_word_rank,s1_read$value)
cor.test(s1_read$aroused_rank,s1_read$value)
cor.test(s1_read$novelty_rank,s1_read$value)
cor.test(s1_read$controversial_rank,s1_read$value)
cor.test(s1_read$ln_emotionality_word_rank,s1_read$value)

leveneTest(s1_read$efficacy,s1_read$value)
t.test(s1_read$value[s1_read$efficacy==0],s1_read$value[s1_read$efficacy==1],var.equal = T)
```


Study 2
```{r}
cor.test(s2_abstract$positivity_sv_rank,s2_abstract$value)

leveneTest(s2_abstract$value,s2_abstract$disease)
t.test(s2_abstract$value[s2_abstract$disease==0],s2_abstract$value[s2_abstract$disease==1],var.equal = T)

cor.test(s2_abstract$useful_rank,s2_abstract$value)
cor.test(s2_abstract$positivity_word_rank,s2_abstract$value)
cor.test(s2_abstract$aroused_rank,s2_abstract$value)
cor.test(s2_abstract$novelty_rank,s2_abstract$value)
cor.test(s2_abstract$controversial_rank,s2_abstract$value)
cor.test(s2_abstract$ln_emotionality_word_rank,s2_abstract$value)

leveneTest(s2_abstract$efficacy,s2_abstract$value)
t.test(s2_abstract$value[s2_abstract$efficacy==0],s2_abstract$value[s2_abstract$efficacy==1],var.equal = T)
```